Supporting Information

### 2018-03-03 SupportingInformation.Rmd
added P functionality to C/N analysis

#initialize
npa_res_CN<-data.frame(Statistic=c("Kendall","Spearman","Corl","Coru","CorlmCoru","Corlt0p1","Corgt0p9","Corlt0p1mCorgt0p9","D2l","D2u","D2umD2l","D2lt0p1","D2gt0p9","D2lt0p9mD2gt0p1"),Value=NA,Frac_of_K_surr_gt_val=NA,Frac_of_S_surr_gt_val=NA)

#utility function
calcstats<-function(v)
{
  h1<-Corbds(v[,1],v[,2],0,.5)
  h2<-Corbds(v[,1],v[,2],0.5,1)
  h3<-Corbds(v[,1],v[,2],0,.1)
  h4<-Corbds(v[,1],v[,2],0.9,1)
  h5<-D2bds(v[,1],v[,2],0,.5)
  h6<-D2bds(v[,1],v[,2],0.5,1)
  h7<-D2bds(v[,1],v[,2],0,.1)
  h8<-D2bds(v[,1],v[,2],0.9,1)
  return(c(cor(v[,1],v[,2],method="kendall"),
           cor(v[,1],v[,2],method="spearman"),
           h1,h2,h1-h2,
           h3,h4,h3-h4,
           h5,h6,h6-h5,
           h7,h8,h8-h7
  ))
}

@@

<!--Display the table generated above-->
```{r table_stat_soilCN, echo=F, results="asis"}
table_nums("table_stat_soilCN",display=F)
knitr::kable(npa_res_CN,caption = "Results of non-parametric tests of tail dependence and asymmetry of tail dependence for the soil C and N dataset. Names of statistics and values on the actual C and N data are listed in the first two columns. The third (respectively, fourth) column is the fraction of Kendall-preserving (respectively, Spearman-preserving) surrogate datasets for which the given statistic is greater than its value on the real data. So if these quantities are smaller than 0.025 the statistic is significantly larger than expected based on null hypotheses of normal copulas; if larger than 0.975, significantly smaller.")
```

>>>>

#initialize
npa_res_CN<-data.frame(Statistic=c("Kendall","Spearman",
  "Corl","Coru","CorlmCoru","Corlt0p1","Corgt0p9","Corlt0p1mCorgt0p9",
  "D2l","D2u","D2umD2l","D2lt0p1","D2gt0p9","D2lt0p9mD2gt0p1",
  "Pl","Pu","PlmPu","Plt0p1","Pgt0p9","Plt0p1mPgt0p9"),
  Value=NA,Frac_of_K_surr_gt_val=NA,Frac_of_S_surr_gt_val=NA)

#utility function
calcstats<-function(v)
{
  h1<-Corbds(v[,1],v[,2],0,.5)
  h2<-Corbds(v[,1],v[,2],0.5,1)
  h3<-Corbds(v[,1],v[,2],0,.1)
  h4<-Corbds(v[,1],v[,2],0.9,1)
  h5<-D2bds(v[,1],v[,2],0,.5)
  h6<-D2bds(v[,1],v[,2],0.5,1)
  h7<-D2bds(v[,1],v[,2],0,.1)
  h8<-D2bds(v[,1],v[,2],0.9,1)
  h9<-Pbds(v[,1],v[,2],0,0.5)$abs_res
  h10<-Pbds(v[,1],v[,2],0.5,1)$abs_res
  h11<-Pbds(v[,1],v[,2],0,0.1)$abs_res
  h12<-Pbds(v[,1],v[,2],0.9,1)$abs_res
  return(c(cor(v[,1],v[,2],method="kendall"),
           cor(v[,1],v[,2],method="spearman"),
           h1,h2,h1-h2,
           h3,h4,h3-h4,
           h5,h6,h6-h5,
           h7,h8,h8-h7,
           h9,h10,h9-h10,
           h11,h12,h11-h12
  ))
}

@@

<!--Display the table generated above-->
```{r table_stat_soilCN, echo=F, results="asis"}
table_nums("table_stat_soilCN",display=F)
knitr::kable(npa_res_CN,caption = "Results of non-parametric tests of tail dependence and asymmetry of tail dependence for the soil C and N dataset. Names of statistics and values on the actual C and N data are listed in the first two columns. The third (respectively, fourth) column is the fraction of Kendall-preserving (respectively, Spearman-preserving) surrogate datasets for which the given statistic is greater than its value on the real data. So if these quantities are smaller than 0.025 the statistic is significantly larger than expected based on a null hypotheses of normal copulas; if larger than 0.975, significantly smaller.")
```

<!--Now need a chunk that calculated D2 for lb=0.1*n, ub=0.1*(n+1) for n=0,...,9, and get 
a bunch of surrogates and calculates the same quantities and then makes a bunch of box-whisker
plots and compares the real data to those for each of these lb/up limits. -->
